Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-11 paper.tex
chore: change the picture following lukas' suggestionsù

  For each time step, a graph is constructed from the environment, and it will associate each node with a local feature (hexagons in the picture). 

@@

  \lukas{should we have numbers at each step in the figure (and then referring in the caption and text)?}

>>>>

  For each time step $t$, a graph is constructed from the environment, and it will associate each node with a local feature (hexagons in the picture). 

@@

  %\lukas{should we have numbers at each step in the figure (and then referring in the caption and text)?}
